### 2025-04-30 tutorials/getstarted.qmd
Fix date in tutorial.

```{julia}
#| code-fold: true
#| echo: false
using Pkg
Pkg.status()
```
```{julia}
#| code-fold: true
#| echo: false
#| output: asis
using Dates
println("This tutorial was last rendered $(Dates.format(now(), "U d, Y, H:M:S")).");
```

>>>>

```{julia}
#| code-fold: true
#| echo: false
using Pkg
Pkg.status()
```
```{julia}
#| code-fold: true
#| echo: false
#| output: asis
using Dates
println("This tutorial was last rendered $(Dates.format(now(), "U d, Y, HH:MM:SS")).");
```
